% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\documentclass[
  11pt,
]{article}
\usepackage{xcolor}
\usepackage{amsmath,amssymb}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
% Shared preamble for the LAMMPS-CO manuscript, supplementary, and cover letter.
% Compiled with xelatex. Latin Modern is used rather than a system font so the
% build is reproducible on any TeX installation; the characters it lacks
% (Greek, super/subscripts, arrows, a few symbols) are mapped explicitly below.
\usepackage{fontspec}
\setmainfont{Latin Modern Roman}
\setsansfont{Latin Modern Sans}
\setmonofont{Latin Modern Mono}[Scale=0.85]

\usepackage[a4paper,margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{graphicx}
\usepackage{amsmath,amssymb}
\usepackage[table]{xcolor}
\usepackage[hidelinks,breaklinks=true]{hyperref}
\usepackage{microtype}
\usepackage{newunicodechar}

% Characters that appear in the text but not in Latin Modern's text font.
\newunicodechar{λ}{\ensuremath{\lambda}}
\newunicodechar{Δ}{\ensuremath{\Delta}}
\newunicodechar{ε}{\ensuremath{\varepsilon}}
\newunicodechar{σ}{\ensuremath{\sigma}}
\newunicodechar{ρ}{\ensuremath{\rho}}
\newunicodechar{τ}{\ensuremath{\tau}}
\newunicodechar{φ}{\ensuremath{\varphi}}
\newunicodechar{δ}{\ensuremath{\delta}}
\newunicodechar{α}{\ensuremath{\alpha}}
\newunicodechar{θ}{\ensuremath{\theta}}
\newunicodechar{→}{\ensuremath{\rightarrow}}
\newunicodechar{≈}{\ensuremath{\approx}}
\newunicodechar{√}{\ensuremath{\sqrt{}}}
\newunicodechar{∫}{\ensuremath{\int}}
\newunicodechar{⟨}{\ensuremath{\langle}}
\newunicodechar{⟩}{\ensuremath{\rangle}}
\newunicodechar{■}{\ensuremath{\blacksquare}}
\newunicodechar{⁺}{\ensuremath{^{+}}}
\newunicodechar{⁻}{\ensuremath{^{-}}}
\newunicodechar{⁰}{\ensuremath{^{0}}}
\newunicodechar{⁴}{\ensuremath{^{4}}}
\newunicodechar{⁵}{\ensuremath{^{5}}}
\newunicodechar{⁶}{\ensuremath{^{6}}}
\newunicodechar{⁷}{\ensuremath{^{7}}}
\newunicodechar{₀}{\ensuremath{_{0}}}
\newunicodechar{₁}{\ensuremath{_{1}}}
\newunicodechar{₂}{\ensuremath{_{2}}}
\newunicodechar{₃}{\ensuremath{_{3}}}
\newunicodechar{₄}{\ensuremath{_{4}}}
\newunicodechar{₆}{\ensuremath{_{6}}}

% pandoc emits this when a document mixes tables and lists
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% Long tables of file names need to break across pages
\setlength{\LTleft}{0pt}
\setlength{\LTright}{0pt}
\renewcommand{\arraystretch}{1.15}

\setlength{\parskip}{0.6em}
\setlength{\parindent}{0pt}
\sloppy
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
% fallback for those not using the hyperref driver hyperxmp:
\makeatletter
\@ifundefined{xmpquote}{\newcommand{\xmpquote}[1]{#1}}{}
\makeatother
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}

\begin{document}

\section{Cover Letter}\label{cover-letter}

\textbf{Chun-Yeol You} Department of Physics and Chemistry DGIST (Daegu
Gyeongbuk Institute of Science and Technology) Daegu, Republic of Korea
cyyou@dgist.ac.kr

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\textbf{To the Editors of \emph{Computer Physics Communications}}

Dear Editors,

I submit for your consideration the manuscript \textbf{``LAMMPS-CO:
extended OpenMP coverage and compiler-friendly force kernels for 261
LAMMPS pair styles''} as a Computer Programs in Physics (CPiP) paper.

\subsection{What the program does}\label{what-the-program-does}

LAMMPS parallelizes across MPI ranks by spatial decomposition, but
within a rank a pair style is threaded only if an OpenMP variant of that
style exists --- and fewer than half of the 307 pair styles have one. On
a many-core node, a simulation using one of the remaining styles leaves
most of the node idle. Separately, the serial force kernels are written
in a form the compiler cannot vectorize: positions and forces are
reached through unqualified \texttt{double\ **} pointers, so aliasing
cannot be ruled out, and the per-atom force array is updated inside the
innermost loop, creating a loop-carried dependence.

LAMMPS-CO addresses both. It supplies 36 new OpenMP pair-style variants,
raising coverage from 157 to 193 of 307 styles, and rewrites the force
kernels of 225 further pair files across 38 packages to use
\texttt{\_\_restrict\_\_}-qualified typed pointers and local
accumulators. Redundant \texttt{pow()} evaluations are removed from the
\texttt{nm/cut}, \texttt{lj/pirani}, and \texttt{mie/cut} families.
Measured gains are 4.31× at four OpenMP threads and 4.93× at eight on a
32,000-atom benchmark, 4--8\% on pair time from the kernel rewrite, and
19.9--40.8\% within the styles where \texttt{pow()} was eliminated.

\subsection{Why it belongs in CPC}\label{why-it-belongs-in-cpc}

The program is a direct, reusable contribution to the most widely used
open-source molecular dynamics engine, and it targets a gap that affects
every LAMMPS user running a style without an accelerated variant. It
also illustrates a programming technique of current interest to the
computational physics community: the code was generated with the
assistance of a large language model coding agent, working from the
reference implementations already present in the OPENMP and OPT
packages. We report that protocol, its measured error rate, and ---
importantly --- the verification that caught its errors.

That verification is the part I would draw your attention to. Rather
than assert numerical equivalence, we build the unmodified and modified
trees from the same LAMMPS commit and run both through LAMMPS's own
\texttt{unittest/force-styles} regression suite: 325 pair-style tests,
identical outcomes. Eleven modified styles are not reachable by that
suite; we distribute dedicated decks and a comparison harness for those,
so every modified style is checked. The process found ten files that did
not compile in packages absent from our original build, one file whose
force expression had a multiplication transcribed as a division, and
three files where the rewrite did not preserve operation order --- the
last of which we reverted rather than ship. All of this is reported in
the manuscript. We take the view that a software paper is more useful
for saying what the verification found than for claiming it found
nothing.

The exercise also surfaced a defect in unmodified LAMMPS:
\texttt{pair\_style\ hybrid/overlay\ kolmogorov/crespi/z} aborts under
\texttt{-sf\ omp}, because \texttt{hybrid/overlay} is registered under
two names and the sub-style tests
\texttt{force-\textgreater{}pair\_style} for exact equality. The
upstream test suite cannot see this, as the OpenMP branch is skipped
when no OMP variant of the sub-style exists. We have submitted the fix
upstream as LAMMPS pull request \#5099.

\subsection{Availability}\label{availability}

The code is public at \url{https://github.com/mirryou-maker/lammps-CO}
under GPLv2, matching LAMMPS, and is being deposited in the CPC Program
Library on Mendeley Data. It applies to an existing LAMMPS tree with a
single script and needs no build-system changes. The complete file-level
inventory of modified styles, the verification decks, and the benchmark
harness are distributed with it.

\subsection{Statements}\label{statements}

This manuscript is original, is not under consideration elsewhere, and
has not been published previously. An earlier version was submitted to
\emph{Archives of Computational Methods in Engineering} and declined
without review as outside that journal's scope (it publishes
state-of-the-art reviews); it has not been peer reviewed. The author
declares no competing interests.

Thank you for considering this submission.

Sincerely,

Chun-Yeol You DGIST

\end{document}
